Document Expansion with External Collections for Information Retrieval

### 2016-08-30 paper.tex
added some introduction

@@

\subsubsection{Query Likelihood}

@@

\subsubsection{Relevance Modeling}

@@

\subsection{Combining Evidence}\label{section.combining.evidence}

>>>>

When using language models (LMs) to perform document retrieval, we treat the query and document texts as observations from unseen (and unobservable) probabilistic processes. In the query likelihood (QL) retrieval model, we rank each document by the likelihood that its language model would ``generate'' the query text. However, if the query is a sample from an underlying stochastic process, it is generally too sparse to fully represent an informtion need.

Relevance modeling is an extremely influential pseudo-relevance feedback technique that helps to allievate the problem of vocabulary mismatch. Instead of assuming that queries are observations sampled from \textit{document} models, we assume that both queries and documents are observations sampled from a \textit{relevance} model (RM) \cite{Lavrenko2001}. We can use this idea to expand the query representation into an estimate of the relevance model as explained in Section \ref{section.expanding.model.rm} and rank documents by the similarity of their estimated language model to the estimated RM.

As a form of pseudo-relevance feedback, part of the relevance modeling process involves assuming that top-ranked documents are relevant to the query. Although this assumption is generally untrue, it is true of enough top-ranked documents that the estimated RM will be of good quality. That is, initially retrieved documents provide a good estimate of the underlying relevance model \textit{in their aggregate}; taken individually, documents are not assumed to accurately represent the underlying RM.

We suggest that, given that a top-ranked document is, like a query, considered a limited observation of terms from a relevance model, documents may be expanded to better reflect their underlying relevance model. In this paper, we propose a method of document expansion that closely mirrors the process of relevance modeling. This document expansion process serves many of the same roles as traditional relevance modeling without excluding the use of RMs; indeed, our document expansion process is complementary to query expansion.

\textbf{Talk about external collections and combining evidence.}

@@

\subsubsection{Query Likelihood}\label{section.expanding.model.ql}

@@

\subsubsection{Relevance Modeling}\label{section.expanding.model.rm}

@@

\subsection{Combining Evidence}\label{section.combining}
